The Unified Nature of the Dielectric Properties of Two-Dimensional Materials

### 2018-11-13 paper.tex
Change until the anisotropy part

% \section{Introduction}
% \label{sec:org2ea169d}
% \linenumbers{}

@@

In short, we have revealed the 2D analog of the Moss relation by both
theoretical modeling and first principles calculations:
$\alpha_{\mathrm{2D}}^{\parallel}$ is inversely proportional to the
minimal bandgap $E_{\mathrm{g}}$, while $\alpha_{\mathrm{2D}}^{\perp}$
is the characteristic thickness of the 2D material. Next we show,
despite their different forms, both 2D Moss-like relations stem from
the same origin. In merit of the unit analysis,
$\alpha_{\mathrm{2D}}^{\parallel}$ and $\alpha_{\mathrm{2D}}^{\perp}$
both have unit of $4\pi\varepsilon_{0} \cdot$[Length], or in other
words, $\alpha_{\mathrm{2D}}^{\parallel}$ and
$\alpha_{\mathrm{2D}}^{\perp}$ correspond to in- and out-of-plane
characteristic lengthes, respectively. The in-plane screened
electrostatic potential $V(r)$ from a point charge in an 2D plane, as
a function of distance $r$:
$V(r) = {\displaystyle \frac{e}{4 \alpha^{\parallel}}}
\left[H_{0}({\displaystyle \frac{2\varepsilon_{0}
      r}{\alpha^{\parallel}}}) - Y_{0}( {\displaystyle \frac{2
      \varepsilon_{0}r}{\alpha^{\parallel}}})\right]$
\cite{Keldysh_1979_eps_multi,Pulci_2014}, where $H_{0}$ is the Struve
function and $Y_{0}$ is the Bessel function of second kind, is
associated with the in-plane screening radius
$r_{0}^{\parallel}=\alpha_{\mathrm{2D}}^{\parallel}/(2
\varepsilon_{0})$, such that $V(r,r/r^{\parallel}_{0} \gg 1)$ reduces
to the simple Coulombic potential in vacuum. Combining with the result
that $\alpha_{\mathrm{2D}}^{\perp}/\varepsilon_{0}$ characterizes the
thickness of a 2D material, we have drawn a generalized picture of the
dielectric nature of 2D materials via the 2D polarizability: the
dielectric screening of a point charge sitting in the middle of a 2D
material can be viewed as an ellipsoid with the length of principle
axes to be
$r_{0}^{\parallel} = \alpha_{\mathrm{2D}}^{\parallel}/(2
\varepsilon_{0})$ and
$r_{0}^{\perp} = \alpha^{\perp}_{\mathrm{2D}}/(2 \varepsilon_{0})$,
respectively, analog to the polarizability ellipsoid picture of
molecules used in spectroscopy \cite{Banwell_1994} (see Supplementary
Figure S12). The polarizability ellipsoid for a 2D material is in
general ultra flat, with $r_{0}^{\parallel} \gg r_{0}^{\perp}$, as
can be seen from the group 6 TMDCs in Table \ref{tbl:radii}.
Moreover, $r_{0}^{\parallel}$ is generally larger for a smaller
bandgap semiconductor, which qualitatively explains the inverse
propotional relation between $\alpha^{\parallel}$ and
$E_{\mathrm{g}}$, a 2D version of the Moss-relation.

@@

The universal Moss-like relation shown in the previous sections
provides general understanding of the dielectric nature of 2D
materials. Moreover, the underlying physical mechanism allows us to
further bridge the 2D and 3D dielectric and electronic properties. As
described in the previous section, the 2D Moss-like relation between
$\alpha^{\parallel}$ and $E_{g}$ is similar to the 3D Moss relation
between $\varepsilon$ and $E_{g}$, with a different power law. Such
difference in the power law can indeed be explained by modern theory
of dielectric properties.  Extend the approach
Eq. \ref{eq:alpha_perp_RPA} to the bulk material, and use the Bloch
presentation for wavefunctions in all dimensions, we derive (detailed
procedure see Supplementary Section S4):
\begin{equation}
  \label{eq:alpha-Eg-3D}
  \begin{aligned}[t]
  \varepsilon_{\mathrm{bulk}} &= 1 + \frac{2e^{2}}{\varepsilon_{0}(2\pi)^{3}}\int d^{3}\mathbf{k}
  \frac{|<u_{\mathrm{v}}(\mathbf{k})|\nabla|u_{\mathrm{v}}(k)>|^{2}}
  {E_{\mathrm{c}}(\mathbf{k}) - E_{\mathrm{v}}(\mathbf{k})} \\
  &\propto E_{g}^{-\frac{1}{2}},\ \mathrm{when}\ \varepsilon_{\mathrm{Bulk}} \gg 1
\end{aligned}
\end{equation}
which recovers the 3D Moss relation. Therefore, the universal
$\alpha^{\parallel}-E_{\mathrm{g}}$ relation is indeed the Moss
relation in 2D world, while the power law of $E_{\mathrm{g}}$ and
independence of effective mass is a result of the confinement
perpendicular to the 2D plane.

The relation between 2D polarizability and 3D dielectric constant
shown in Eqs. \ref{eq:alpha-para-def} and \ref{eq:alpha-perp-def} can
be further used to reconstruct the dielectric
constants $\varepsilon^{\parallel}_{\mathrm{Bulk}}$ and
$\varepsilon^{\perp}_{\mathrm{Bulk}}$ of a bulk layered material from
$\alpha^{\parallel}$ and $\alpha^{\perp}$ of the monolayer (see Figure
\ref{fig-4}a). First, we see that the 2D polarizabilities for
individual layers in the bulk materials
$\alpha_{\mathrm{Bulk}}^{\parallel}$ and
$\alpha_{\mathrm{Bulk}}^{\perp}$, can be calculated using
Eqs. \ref{eq:alpha-para-def} and \ref{eq:alpha-perp-def}, when $L$
becomes the bulk interlayer distance $L_{\mathrm{Bulk}}$. The
dielectric constants of the bulk material are then expressed as:
\begin{subequations}
\begin{eqnarray}
  \label{eq:3D-para}
  &\varepsilon^{\parallel}_{\mathrm{Bulk}} &= 1 + {\displaystyle \frac{\alpha_{\mathrm{bulk}}^{\parallel}}{\varepsilon_{0} L_{\mathrm{Bulk}}}}\\
  \label{eq:3D-perp}
  &\varepsilon^{\perp}_{\mathrm{Bulk}} &= \left(1 - \frac{\alpha_{\mathrm{Bulk}}^{\perp}}{\varepsilon_{0} L_{\mathrm{Bulk}}}\right)^{-1}
\end{eqnarray}
\end{subequations}
Note that $\alpha_{\mathrm{Bulk}}^{\parallel}$ and
$\alpha_{\mathrm{Bulk}}^{\perp}$ may not essentially be the same as
$\alpha$ of isolated layer, but still quite close as seen in Figure
\ref{fig-3}b and \ref{fig-3}c. Nevertheless we will first see how good
we can predict $\varepsilon_{\mathrm{Bulk}}^{\parallel}$ and
$\varepsilon_{\mathrm{Bulk}}^{\perp}$, when assuming
$\alpha_{\mathrm{bulk}}=\alpha$. We compare
$\varepsilon_{\mathrm{bulk}}^{\parallel}$ and
$\varepsilon_{\mathrm{bulk}}^{\perp}$ from first principles DFT
calculations compared with the values predicted using Eqs
\ref{eq:3D-para} and \ref{eq:3D-perp}, as show in Figure \ref{fig-4}b
and \ref{fig-4}c, respectively. Data calculated at both HSE06 and PBE
levels which give almost identical trends, indicating the generality
of such approach. Note although the stacking order is not considered
in Eqs. \ref{eq:3D-para} and \ref{eq:3D-perp}, we found that the
influence of stacking is minor (see Supplementary Figure SXX
\todo{Wait for Declan's data}). We observe that the majority of
predicted $\varepsilon_{\mathrm{bulk}}^{\parallel}$ values align along
the line $y=x$ , with a linear regression slope of 1.01 and $R^2$ of
0.97, indicating that such method indeed captures the transition from
$\alpha^{\parallel}$ to $\varepsilon_{\mathrm{Bulk}}^{\parallel}$. On
the other hand, we observe the predicted values of
$\varepsilon_{\mathrm{bulk}}^{\perp}$ has good agreement with the DFT
values when $E_{\mathrm{g}}>4$ eV, while the deviation becomes larger
when $E_{\mathrm{g}}$ reduces. The difference for the prediction of
$\varepsilon^{\parallel}$ and $\varepsilon^{\perp}$ means that
$\alpha^{\parallel}_{\mathrm{Bulk}}$ can generally be estimated from
its 2D counterpart, while $\alpha^{\perp}_{\mathrm{Bulk}}$ differs due
to interlayout coupling and overlap between induced dipoles, as also
observed in Figure \ref{fig-3}b, \ref{fig-3}c, and other studies
\cite{Andersen_2015_dielec_vdWH,Laturia_2018}. With a better model
describing $\alpha_{\mathrm{bulk}}^{\perp}$ as function of
$\alpha^{\perp}$ and the degree of interlayer coupling \cite{Tkatchenko_2012}, the dielectric transition from 2D to 3D would
be smoothly described.

>>>>

% \section{Introduction}
% \label{sec:org2ea169d}
\linenumbers{}

@@

In short, we have revealed the 2D analog of the Moss relation by both
theoretical modeling and first principles calculations:
$\alpha_{\mathrm{2D}}^{\parallel}$ is inversely proportional to the
minimal bandgap $E_{\mathrm{g}}$, while $\alpha_{\mathrm{2D}}^{\perp}$
is the characteristic thickness of the 2D material. Next we show,
despite their different forms, both 2D Moss-like relations stem from
the same origin. In merit of the unit analysis,
$\alpha_{\mathrm{2D}}^{\parallel}$ and $\alpha_{\mathrm{2D}}^{\perp}$
both have unit of $4\pi\varepsilon_{0} \cdot$[Length], or in other
words, $\alpha_{\mathrm{2D}}^{\parallel}$ and
$\alpha_{\mathrm{2D}}^{\perp}$ correspond to in- and out-of-plane
characteristic lengthes, respectively. The in-plane screened
electrostatic potential $V(r)$ from a point charge in an 2D plane, as
a function of distance $r$:
$V(r) = {\displaystyle \frac{e}{4 \alpha^{\parallel}}}
\left[H_{0}({\displaystyle \frac{2\varepsilon_{0}
      r}{\alpha^{\parallel}}}) - Y_{0}( {\displaystyle \frac{2
      \varepsilon_{0}r}{\alpha^{\parallel}}})\right]$
\cite{Keldysh_1979_eps_multi,Pulci_2014}, where $H_{0}$ is the Struve
function and $Y_{0}$ is the Bessel function of second kind, is
associated with the in-plane screening radius
$r_{0}^{\parallel}=\alpha_{\mathrm{2D}}^{\parallel}/(2
\varepsilon_{0})$, such that $V(r,r/r^{\parallel}_{0} \gg 1)$ reduces
to the simple Coulombic potential in vacuum. Combining with the result
that $\alpha_{\mathrm{2D}}^{\perp}/\varepsilon_{0}$ characterizes the
thickness of a 2D material, we have drawn a generalized picture of the
dielectric nature of 2D materials via the 2D polarizability: the
dielectric screening of a point charge sitting in the middle of a 2D
material can be viewed as an ellipsoid with the length of principle
axes to be
$r_{0}^{\parallel} = \alpha_{\mathrm{2D}}^{\parallel}/(2
\varepsilon_{0})$ and
$r_{0}^{\perp} = \alpha^{\perp}_{\mathrm{2D}}/(2 \varepsilon_{0})$,
respectively, analog to the polarizability ellipsoid picture of
molecules used in spectroscopy \cite{Banwell_1994} (see Supplementary
Figure S12). The polarizability ellipsoid for a 2D material is in
general ultra flat, with $r_{0}^{\parallel} \gg r_{0}^{\perp}$, as
can be seen from the group 6 TMDCs in Table \ref{tbl:radii}.
Moreover, $r_{0}^{\parallel}$ is generally larger for a smaller
bandgap semiconductor, which qualitatively explains the inverse
propotional relation between $\alpha_{\mathrm{2D}}^{\parallel}$ and
$E_{\mathrm{g}}$, a 2D version of the Moss-relation.

@@

The universal Moss-like relation shown in the previous sections
provides general understanding of the dielectric nature of 2D
materials. Moreover, the underlying physical mechanism allows us to
further bridge the 2D and 3D dielectric and electronic properties in
various ways. Using the similar appraoch as we derive the 2D Moss-like
relations, we show that the
$\alpha_{\mathrm{2D}}^{\parallel} \propto E_{\mathrm{g}}^{-1}$
relation for a 2D material naturally transforms to
$\varepsilon \propto E_{\mathrm{g}}^{-\frac{1}{2}}$ for a bulk
semiconductor, which is the original Moss relation (details see
Supplementary Section SXX \todo{note}). In other words, the proposed
$\alpha_{\mathrm{2D}}^{\parallel}-E_{\mathrm{g}}$ relation is indeed
the Moss relation in 2D world, while the different power law for
$E_{\mathrm{g}}$ is caused by the electronic confinement.

% As described in the previous section, the 2D Moss-like relation
% between $\alpha^{\parallel}$ and $E_{g}$ is similar to the 3D Moss
% relation between $\varepsilon$ and $E_{g}$, with a different power
% law. Such difference in the power law can indeed be explained by
% modern theory of dielectric properties.  Extend the approach
% Eq. \ref{eq:alpha_perp_RPA} to the bulk material, and use the Bloch
% presentation for wavefunctions in all dimensions, we derive (detailed
% procedure see Supplementary Section S4):
% \begin{equation}
  % \label{eq:alpha-Eg-3D}
  % \begin{aligned}[t]
  % \varepsilon_{\mathrm{bulk}} &= 1 + \frac{2e^{2}}{\varepsilon_{0}(2\pi)^{3}}\int d^{3}\mathbf{k}
  % \frac{|<u_{\mathrm{v}}(\mathbf{k})|\nabla|u_{\mathrm{v}}(k)>|^{2}}
  % {E_{\mathrm{c}}(\mathbf{k}) - E_{\mathrm{v}}(\mathbf{k})} \\
  % &\propto E_{g}^{-\frac{1}{2}},\ \mathrm{when}\ \varepsilon_{\mathrm{Bulk}} \gg 1
% \end{aligned}
% \end{equation}
% which recovers the 3D Moss relation.

The dielectric constant $\varepsilon$, although not well-defined for
monolayer 2D material, becomes applicable when the 2D layers are
stacked. \todo[inline]{I would appreciate for polishing this sentence}
In a bulk layered materil stacked by layers with equilibrium
inter-layer distance $L_{\mathrm{Bulk}}$, we define the polarizability
of individual layer $\alpha_{\mathrm{2D}}(L=L_{\mathrm{Bulk}})$ as
$\alpha_{\mathrm{Bulk}}$. Inspired by Eqs. \ref{eq:alpha-para-def} and
\ref{eq:alpha-perp-def}, the dielectric constants
$\varepsilon^{\parallel}_{\mathrm{Bulk}}$ and
$\varepsilon^{\perp}_{\mathrm{Bulk}}$ of a bulk layered material, can
be reconstructed by $\alpha_{\mathrm{Bulk}}^{\parallel}$ and
$\alpha_{\mathrm{Bulk}}^{\perp}$ (see Figure \ref{fig-4}a):
\begin{subequations}
\begin{align}
  \label{eq:3D-para}
  \varepsilon^{\parallel}_{\mathrm{Bulk}}
  &= 1 + \frac{\alpha_{\mathrm{bulk}}^{\parallel}}{\varepsilon_{0} L_{\mathrm{Bulk}}}
  \approx 1 + \frac{\alpha_{\mathrm{2D}}^{\parallel}}{\varepsilon_{0} L_{\mathrm{Bulk}}} \\
  \label{eq:3D-perp}
  \varepsilon^{\perp}_{\mathrm{Bulk}}
  &= \left(1 - \frac{\alpha_{\mathrm{Bulk}}^{\perp}}{\varepsilon_{0} L_{\mathrm{Bulk}}}\right)^{-1}
  \approx \left(1 - \frac{\alpha_{\mathrm{2D}}^{\perp}}{\varepsilon_{0} L_{\mathrm{Bulk}}}\right)^{-1}
\end{align}
\end{subequations}
The approximations come from the fact that
$\alpha_{\mathrm{Bulk}} \approx \alpha_{\mathrm{2D}}$, which can be
seen from the results of Figure \ref{fig-3}b and \ref{fig-3}c.  Note
that the effect of stacking is not considered in Eqs. \ref{eq:3D-para}
and \ref{eq:3D-perp}. We compare the values of
$\varepsilon_{\mathrm{bulk}}^{\parallel}$ and
$\varepsilon_{\mathrm{bulk}}^{\perp}$ from DFT calculations (y-axis)
with those predicted using Eqs \ref{eq:3D-para} and \ref{eq:3D-perp}
(x-axis), as show in Figure \ref{fig-4}b and \ref{fig-4}c,
respectively, with data calculated at both HSE06 and PBE levels give
almost identical trends. We observe that
$\varepsilon_{\mathrm{bulk}}^{\parallel}$ values calculated by DFT and
predicted by Eq. \ref{eq:3D-para} align along the line $y=x$ , with a
linear regression slope of 1.01 and $R^2$ of 0.97. On the other hand,
$\varepsilon_{\mathrm{bulk}}^{\perp}$ values predicted from
Eq. \ref{eq:3D-perp} agree well with the DFT-calculated values when
$E_{\mathrm{g}}>4$ eV, while the deviation becomes larger when
$E_{\mathrm{g}}$ reduces. The difference for the prediction of
$\varepsilon^{\parallel}$ and $\varepsilon^{\perp}$ means that
$\alpha^{\parallel}_{\mathrm{Bulk}}$ can generally be estimated from
its 2D counterpart, while $\alpha^{\perp}_{\mathrm{Bulk}}$ differs due
to interlayout coupling and overlap between induced
dipoles\cite{Andersen_2015_dielec_vdWH,Laturia_2018}, as also observed
in Figure \ref{fig-3}b, \ref{fig-3}c . With a better model describing
$\alpha_{\mathrm{bulk}}^{\perp}$ as function of $\alpha^{\perp}$ and
the degree of interlayer coupling, the dielectric transition from 2D
to 3D would be smoothly described.
